### 2021-05-04 thesis/tex/ICtheory.tex
update

\documentclass[draft=True]{thesis}
\usepackage{graphicx, slashed, siunitx}
\usepackage[utf8]{inputenc}
\usepackage{xr-hyper}
\input{commands}
\begin{document}

@@

\section{IceCube event count}\label{ch:ICmethod}
%TODO: show IC MC data

The flux comes from \cite{hondapaper} %TODO: talk about flux
The flux data is binned in $\ztrue$ and has the following form

\begin{tabular}{lrrrrrrr}
    %\toprule
           $\Etrue$ [\si{\GeV}] &        $\phi_\mu$ &     $\phi_\bar{\mu}$ &        $\phi_e$ &     $\phi_{\bar{e}}$ &  $\ztrue_{min}$ &  $\ztrue_{max}$\\
    %\midrule
       27825.594022 &  6.060061e-12 &  3.167883e-12 &  1.558607e-13 &  1.038747e-13 &   -0.2 &   -0.1 \\
      247707.635599 &  5.940855e-16 &  2.923931e-16 &  1.364937e-17 &  8.115912e-18 &   -0.7 &   -0.6 \\
         22.387000 &  3.328100e-02 &  2.781700e-02 &  9.565800e-03 &  7.149400e-03 &   -0.3 &   -0.2 \\
      432876.128108 &  5.185841e-17 &  2.320702e-17 &  1.456761e-18 &  9.828299e-19 &   -1.1 &   -1.0 \\
       64280.731173 &  1.582403e-13 &  8.095293e-14 &  3.480179e-15 &  2.211758e-15 &   -0.4 &   -0.3 \\
    %\bottomrule
\end{tabular}

The fluxes are averaged over azimuthal direction and over solar minimun/maximum. The units of the fluxes are given as \si{\GeV^-1 \metre^-2 \second^-1 \steradian^-1}. 
We note that the fluxes for $\nt$ and $\nu_\bar{\tau}$ are missing. This is due to the rapid decay (and hence, low flux) of the $\tau$. Thus, we never have to use probabilities on the form 
$P_{\tau \beta}$, since we have no incoming $\nu_\tau$.

After interpolating this data, we can plot the raw data together with its interpolated values.
%TODO: flux interpolated figure.

As the neutrinos have propagated the Earth, they arrive at the South Pole, where they interact in the ice to form their charged leptons. We now are interested in the effective area, i.e.~the detector area that the lepton "sees".
The effective area, $\Aeff$, depends on several parameters, some of them being detector physical volume, $\Etrue$,$\ztrue$ and the neutrino cross-section. Fortunately, the binned $\Aeff$ is provided to us by the ICeCube collaboration~\cite{ICaeff}.
The data file has the following form

\begin{tabular}{lrrrrr}
    %\toprule
    $\Etrue_{min}$ [\si{\GeV}] &     $\Etrue_{max}$ [\si{\GeV}]&   $\ztrue_{min}$ &   $\ztrue_{max}$ &     $\Aeff$ [\si{\metre\squared}] \\
    %\midrule
         251.2 &      316.2 &  -0.92 &  -0.91 &   0.0174 \\
      794300.0 &  1000000.0 &  -0.80 &  -0.79 &  69.3600 \\
        3981.0 &     5012.0 &  -0.78 &  -0.77 &   3.1490 \\
        1585.0 &     1995.0 &  -0.07 &  -0.06 &   0.4659 \\
        398.1 &      501.2 &  -0.73 &  -0.72 &   0.0555 \\
    %\bottomrule
    \end{tabular}
Here, $\Aeff$ has been averaged over $\Aeff_\mu$ and $\Aeff_\bar{\mu}$. Thus, it is not flavor dependent.
Just as with the fluxes, we interpolate this in $\Etrue,\ztrue$ and show the result %TODO aeff interpolation

@@

So how do we then obtain $\sigma_{x^r}(x^t)$ and $\mu(x^t)$ needed to construct the Gaussian? A Monte Carlo sample publically released by the 
collaboration has all the ingredients that we need. %TODO: source.
In Table %TODO: add
we see a snippet of how it looks like.

@@

\begin{figure}[!tb]\label{fig:IC_MC_gpr}
    \begin{center}
       \includegraphics[width=0.4\linewidth]{figures/IC_MC_gpr.pdf} %TODO: another fig here? Aeff?
    \end{center}
    \caption{Relationship between the true and reconstructed muon energy in the IceCube MC sample~\cite{IC2016}}\label{fig:IC_MC_counts}. Shaded area shows the $99.9$th percentile limits predicted by the regressor trained on this set.
 \end{figure}

\end{document}

>>>>

\documentclass{thesis}
\usepackage[margin=0.5in]{geometry}
\input{commands}
\begin{document}
\begin{figure}[t]\label{fig:flux_aeff}
    \includegraphics[width=0.5\textwidth]{figures/flux.pdf}\hspace{-1cm}
    \includegraphics[width=0.5\textwidth]{figures/aeff.pdf}
    \vspace{-2.5cm}\caption{\emph{Left panel:} Interpolated South Pole atmospheric flux with data from~\cite{hondaArticle}.
    \emph{Right panel:} Interpolated IceCube effective area with data from~\cite{ICaeff}.}
\end{figure}

\section{Atmospheric neutrino flux}
The flux comes from \cite{hondaArticle} %TODO: talk about flux
The flux data is binned in $\ztrue$ and a selection is shown in Table~\ref{table:flux}. The fluxes are averaged over azimuthal direction and over solar minimum/maximum. 
The units of the fluxes are given as \si{\per\GeV \per\metre\squared \per\second \per\steradian} and are omitted
from the table for clarity. 
We note that the fluxes for $\nt$ and $\nu_{\bar{\tau}}$ are missing. This is due to the rapid decay (and hence, low flux) of the $\tau$. 
Thus, we never have to use probabilities on the form 
$P_{\tau \beta}$, since we have no incoming atmospheric $\nu_\tau$ flux.

Interpolating the data yields makes us capable of returning all four necessary fluxes for a given true energy and true zenith.
The result is shown in Fig.~\ref{fig:flux_aeff}.

\begin{table}[h]\label{table:flux}
    \begin{center}
        \begin{tabular}{lcccccc}
            \hline \hline
            $\Etrue$ [\si{\GeV}] &$\phi_\mu$ &$\phi_{\bar{\mu}}$ &$\phi_e$ &$\phi_{\bar{e}}$ & $\ztrue_{min}$ &$\ztrue_{max}$\\
            \hline
            27825 &  \SI{6.06e-12}{} &  \SI{3.17e-12}{} &  \SI{1.56e-13}{} &  \SI{1.04e-13}{} &   -0.2 &   -0.1 \\
            247707 &  \SI{5.94e-16}{} &  \SI{2.92e-16}{} &  \SI{1.36e-17}{} &  \SI{8.12e-18}{} &   -0.7 &   -0.6 \\
                22 &  \SI{3.33e-02}{} &  \SI{2.78e-02}{} &  \SI{9.57e-03}{} & \SI{7.15e-03}{} &   -0.3 &   -0.2 \\
            432876 &  \SI{5.19e-17}{} &  \SI{2.32e-17}{} &  \SI{1.46e-18}{} & \SI{9.83e-19}{} &   -1.1 &   -1.0 \\
            64280 &  \SI{1.58e-13}{} &  \SI{8.10e-14}{} &  \SI{3.49e-15}{} &  \SI{2.21e-15}{} &   -0.4 &   -0.3 \\
            \hline
        \end{tabular}
    \end{center}
    \caption{A selection of processed atmospheric South Pole fluxes from~\cite{hondaData} by Honda et al.~\cite{hondaArticle}.}
\end{table}

@@

\section{IceCube event count}\label{ch:ICmethod}
As the neutrinos have propagated the Earth, they arrive at the South Pole, where they interact in the ice to form their charged leptons. We now are interested in the effective area, i.e.~the detector area that the lepton "sees".
The effective area, $\Aeff$, depends on several parameters, some of them being detector physical volume, $\Etrue$,$\ztrue$ and the neutrino cross-section. Fortunately, the binned $\Aeff$ is provided to us by the collaboration~\cite{ICaeff}.
The data file has the following form

\begin{table}\label{table:aeff}
    \begin{tabular}{lrrrrr}
        \hline \hline
        $\Etrue_{min}$ [\si{\GeV}] &     $\Etrue_{max}$ [\si{\GeV}]&   $\ztrue_{min}$ &   $\ztrue_{max}$ &     $\Aeff$ [\si{\metre\squared}] \\
        \hline
             251 &      316 &  -0.92 &  -0.91 &   0.0174 \\
          794300 &  1000000 &  -0.80 &  -0.79 &  69.3600 \\
            3981 &     5012 &  -0.78 &  -0.77 &   3.1490 \\
            1585 &     1995 &  -0.07 &  -0.06 &   0.4659 \\
            398 &      501 &  -0.73 &  -0.72 &   0.0555 \\
        \hline
        \end{tabular}
    \caption{IceCube effective area from~\cite{ICaeff}}
\end{table}

Here, $\Aeff$ has been averaged over $\Aeff_\mu$ and $\Aeff_{\bar{\mu}}$. Thus, it is not flavor dependent.
Just as with the fluxes, we interpolate this in $\Etrue,\ztrue$ and show the result %TODO aeff interpolation

@@

So how do we then obtain $\sigma_{x^r}(x^t)$ and $\mu(x^t)$ needed to construct the Gaussian? A Monte Carlo sample publically released by the 
collaboration has all the ingredients that we need~\cite{IC2016}. In Table.~\ref{table:IC_MC} we show a selection of the data.
The "pdg" column refers to the Monte Carlo particle classification, where 13 is the tag for $\nm$, while -13 refers
to an $\anm$. Here we note a crucial property of the IceCube dataset that will impact our analysis: the MC released by the collaboration
only includes simulated muon events.

\begin{table}\label{table:IC_MC}
    \begin{tabular}{lrrrrr}
        \hline \hline
        pdg &      $\Ereco$ [\si{\GeV}] &     $\zreco$ &       $\Etrue$ [\si{\GeV}] &     $\ztrue$ \\
        \hline
         13 &  1665 & -0.645884 &    592 & -0.653421 \\
         13 &   587 & -0.373241 &    342 & -0.424979 \\
        -13 &  1431 & -0.177786 &   1169 & -0.189949 \\
        -13 &   831 & -0.807226 &   1071 & -0.805559 \\
         13 &   988 & -0.370746 &   1861 & -0.367922 \\
         \hline
  \end{tabular}
  \caption{A selection of the data found in~\ref{IC2016}}
\end{table}

@@

\begin{figure}[!tb]\label{fig:IC_MC_gpr}
    \begin{center}
       \includegraphics[width=0.4\linewidth]{figures/IC_MC_gpr.pdf} %TODO: another fig here? Aeff?
    \end{center}
    \caption{Relationship between the true and reconstructed muon energy in the IceCube MC sample~\cite{IC2016}}\label{fig:IC_MC_counts}. Shaded area shows the $99.9$th percentile limits predicted by the regressor trained on this set.
 \end{figure}
\bibliographystyle{nature}
\bibliography{ref.bib}
\end{document}

### 2021-05-04 thesis/tex/nsiTheory.tex
update

\documentclass[draft=True]{thesis}
\input{commands}
\usepackage{physics,amsmath, amsfonts, siunitx, amssymb, graphicx}
\usepackage[utf8]{inputenc}
\usepackage{xr-hyper}

@@

\section{Non-standard interactions in IceCube}
In our analysis of IceCube, we are constrained to muon track events. Thus, we are not able to test any theory which does not modify $P_{\a \mu}$ directly or 
indirectly. Since all standard matter potentials are diagonal, the elements $\epsilon_{\a\b}, \a = \b$ will directly adjust the matter potential felt 
by flavor $\a$. The off-diagonal terms have a more interesting theoretical implication as the open up matter interactions across flavors. Remember, in the Standard model,
we are restriced to weak interactions that conserve lepton number. However, a off-diagonal NSI parameter allows flavor transitions during matter interactions.
Moreover, $\epsilon_{\a\b}$ modifies the $\nu_\a \to \nu_\b$ transition independently
of the mixing matrix. Thus, we can in theory boost a flavor transition which is supressed by the mixing matrix. Moreover, since the NSI parameters are 6, and the PMNS
matrix is parametrized with only 3 parameters, we have more degrees of freedom when adjusting the probabilities using the NSI matrix.

As discussed in Eq.~\ref{eq:Uvalues}, the atmospheric $\nm \to \nt$ transition will be the most abundant, making $\emt$ and $\emm$ or $\ett$ the most suitable
NSI parameters to constrain.

In Fig.~\ref{fig:IC_NSI_probs}, we plot $\Pmm$ and $\Pamam$ for 3 cases of $\ep$ and $\emt$ each. As is clear from the 
left panels, the value of $\ett$ does not affect neither $\Pmm$ nor $\Pamam$, as we expected. Hence, we will not be able
to say anything about $\ett$ in our study. The right panels show an interesting relationship between the sign of the NSI parameter 
and the neutrino type. $\Pmm$ with positive $\ett$ is the same as $\Pamam$ with negative $\ett$. Looking at the form of the matter potential, 
this is something that we should expect. In the standard interaction framework, we distinguish between neutrinos and antineutrinos by flipping the sign 
of the CC potential. Since the NSI potential has the same form, any sign flipping of the NSI potential will have the same effect as 
having an antineutrino.

\begin{figure}\label{fig:IC_NSI_probs}
    \begin{center}
    \includegraphics[width=1\textwidth, height=0.3\textheight]{figures/IC_NSI_probs.pdf}
    \caption{\emph{Top panels: }$\nm$ survival probability for different cases of the two NSI parameters $\ett$ and $\emt$
    \emph{Bottom panels: }$\anm$ survival probability for different cases of the two NSI parameters $\ett$ and $\emt$.
    In all plots, \ztrue = -1.}
    \end{center}
\end{figure}
\end{document}

>>>>

\documentclass{thesis}
\usepackage[margin=0.5in]{geometry}
\input{commands}
\usepackage{siunitx, graphicx}
\usepackage[utf8]{inputenc}
\usepackage{xr-hyper}

@@

\section{Non-standard interactions in IceCube}
In our analysis of IceCube, we are constrained to muon track events. Thus, we are not able to test any theory which does not modify $P_{\a \mu}$. Moreover,
the IceCube data is avaibable in the range \SI{500}{\GeV} to \SI{10}{\TeV} range, where any rapid oscillations have settled down.

Since all standard matter potentials are diagonal, 
the elements $\epsilon_{\a\b}, \a = \b$ will directly adjust the matter potential felt 
by flavor $\a$. The off-diagonal terms have a more interesting theoretical implication as the open up matter interactions across flavors. Remember, in the Standard model,
we are restriced to weak interactions that conserve lepton number. However, a off-diagonal NSI parameter allows flavor transitions during matter interactions.
Moreover, $\epsilon_{\a\b}$ modifies the $\nu_\a \to \nu_\b$ transition independently
of the mixing matrix. Thus, we can in theory boost a flavor transition which is supressed by the mixing matrix. Moreover, since we have 6 NSI parameters, and the PMNS
matrix is parametrized with only 3 parameters, we have more degrees of freedom when adjusting the probabilities using the NSI matrix. Each term in the PMNS matrix consists of at least
two of the three mixing angles, making them much more dependent on each other.

As discussed in Eq.~\ref{eq:Uvalues}, the atmospheric $\nm \to \nt$ transition will be the most abundant, making $\emt$, $\emm$, $\ett$ the most suitable
NSI parameters to constrain from muon events. As we will see, $\eem$ is also a candidate, alebit a weaker one.

In Fig.~\ref{fig:emt_ett_probs}, we see how the introduction of $\emt = 0.02$ alters the $\nm$ and $\anm$ survival probabilities
for neutrinos that traverse the entire Earth diameter (i.e. $\ztrue = -1$). $\emt$ does not dramatically change neither
amplitude nor frequency of the probabilities. Instead, it seems to strech or compress the oscillations. Since the 
only difference between the way neutrinos and antineutrinos interact with matter is the sign of the potential, the probability for
$\nm$ with positive $\epsilon_{\a\b}$ is identical to the probability for $\anm$ with negative $\epsilon_{\a\b}$. Thus, the dashed line 
in the right panel not only shows the survival probability for $\anm$ with $\emt=0.02$, but also the survival probability for $\nm$ with $\emt=-0.02$.
Hence, we note that $\emt > 0$ stretches (compresses) $\Pmm$ for neutrinos (antineutrinos), while $\emt < 0$ compresses (stretches) $\Pmm$ for neutrinos (antineutrinos).

The value of $\ett$ does not affect neither $\Pmm$ nor $\Pamam$, in the IceCube region above \SI{500}{\GeV}. Hence, we will not be able
to say anything about $\ett$ in our IceCube study.  Comparing the probabilities in Fig.~\ref{fig:emt_ett_probs} with $\ett = 0.05$ with the ones for $\emt = 0.02$ in Fig.~\ref{fig:emt_ett_probs},
we see that even though we let $\ett$ take 2.5 times the value of $\emt$, its effect on $\Pmm$ is smaller. The weakening of the $\Pamam$ resonance will be visible in DeepCore, but we should expect a less stringent 
constraint due to the weakness of the effect compared to $\emt$.

Thus, we will use IceCube to constrain $\emt$ only.

Moving on to $\eem$ and Fig.~\ref{fig:eem_eet_probs}, we see that both probabilities has shifted downwards for $\Etrue > \SI{500}{\GeV}$.
In ~\ref{fig:eem_eet_probs}, we see that the muon channel remains largely unaffected of the value of $\eet$ as we expected. The expection of this lies 
in the DeepCore region of rapid oscillations, where mixing is more violent. 
\begin{figure}\label{fig:emt_ett_probs}
    \begin{center}%TODO subplots and fix labels in parahgraph aboveto match them
        \includegraphics[width=0.45\textwidth]{figures/emt_probs.pdf}
        \includegraphics[width=0.45\textwidth]{figures/ett_probs.pdf}
        \caption{\emph{Left panel:} Muon neutrino and antineutrino survival probabilities for
        $\ztrue = -1$ when $\emt = 0.02$. All other NSI parameters are fixed to zero.
        \emph{Right panel:} Muon neutrino and antineutrino survival probabilities for
        $\ztrue = -1$ when $\ett = 0.05$. All other NSI parameters are fixed to zero.}
    \end{center}
\end{figure}

\begin{figure}\label{fig:eem_eet_probs}
    \begin{center}
        \includegraphics[width=0.45\textwidth]{figures/eem_probs.pdf}
        \includegraphics[width=0.45\textwidth]{figures/eet_probs.pdf}
        \caption{Muon neutrino and antineutrino survival probabilities for
        $\ztrue = -1$\emph{Left panel:} $\eem = 0.2$. All other NSI parameters are fixed to zero.
        \emph{Right panel:} $\eet = 0.2$. All other NSI parameters are fixed to zero.}
    \end{center}
\end{figure}

\section{Non-standard interactions in DeepCore and PINGU}
Now we repeat our proability analysis but for the DeepCore/PINGU region of \SIrange{5.6}{56}{\GeV}. As we previously saw,
we have rapid oscillations, which means that "indirect" modifications (i.e. $\eet$ will affect the $\Pmm$ channel)
will be more apparent, since all flavors are involved to a greater degree compared with the more stable region above \SI{500}{\GeV}, where 
many oscillations have settled down.

Another feature of our DeepCore study includes the fact that we now have access to cascade events, in which $\ne$ and $\nt$ are more abundant. %TODO:show this?
Thus, we are no longer constrained to the $\mu$ channel alone, but we can now find interesting features in the other channels too. However, we 
remember that the $\nm$ flux is still the most abundant. %TODO: link to plot comparison of m and e flux.

Fig.~\ref{fig:emt_ett_probs} shows that $\emt$ affects both $\Pmm$ and $\Pamam$ over the whole energy range. Since 
IceCube also sees this, we hope to be able to boost the constraining of $\emt$ by combining the two experiments.

Regarding $\ett$ in Fig.~\ref{fig:eem_eet_probs}, the signal mainly shows in the $\Pamam$ channel as
a weaker resonance dip in the \SI{20}{\GeV} region. Thus, DeepCore/PINGU alone will be used to constrain this parameter.

$\eem$ in Fig.~\ref{fig:eem_eet_probs} shows weak resonance dampening for both $\nm$ and $\anm$.

For $\eet$, we see a similar resonance dampening in $\Pmm$ as we did with $\ett$ for $\Pamam$. Hence, we should be able to 
see the $\eet$ effect in DeepCore/PINGU, but remember that we now have the option to look at the other flavor channels.

Fig.~\ref{fig:Pee_eet_probs} shows the electron neutrino and antineutrino survival probabilities, and here we see
a clear difference when turning on $\eet$.
%TODO: clean up above and expand a bit.
\begin{figure}\label{fig:Pee_eet_probs}
    \begin{center}
        \includegraphics[width=0.6\textwidth]{figures/Pee_eet_probs.pdf}
        \caption{Electron neutrino and antineutrino survival probabilities for
        $\ztrue = -1$ when $\eet = 0.2$. All other NSI parameters are fixed to zero.}
    \end{center}
\end{figure}

We summarize our findings in Table~\ref{table:nsi}
\begin{table}
    \begin{center}
    \begin{tabular}{lccc}
            \hline \hline & & \multicolumn{2}{c} {\text { Visibility }} \\
            \cline { 3 - 4 } \text {Parameter} & Range & \text { IC } & \text {DC } \\
            \hline
            $\ett$ &$\pm 0.05 $ & $\times$ & \checkmark \\
            $\emt$ &$\pm 0.02 $& \checkmark & \checkmark \\
            $\eem$ &$\pm 0.2 $& \checkmark & \checkmark \\
            $\eet$ &$\pm 0.2 $& $\times$ & \checkmark \\
            \hline
        \label{table:nsi}
    \end{tabular}
    \end{center}
    \caption{Table of NSI parameters and their ranges considered in this study, along with visibility off
    their signal in IceCube (IC) and DeepCore/PINGU (DC).}
\end{table}

\end{document}

### 2021-05-04 thesis/tex/oscillations.tex
update

\documentclass[draft=True]{thesis}
\usepackage{graphicx, slashed}
\usepackage[utf8]{inputenc}
%\usepackage{hyperref}
\usepackage{xr-hyper}
\externaldocument{SM}
\input{commands}
\begin{document}

@@

In this work, we will be using the best-fit values from~\cite{nufit},
\begin{align}\label{eq:nufitparams}
    &\Delta m^2_{21} =  \SI{7.42e-5}{\electronvolt^2},\hspace{0.5em} \Delta m^2_{31} =  \SI{2.517e-3}{\electronvolt^2}, \nonumber \\
    &\theta_{12} = \SI{33.44}{\degree},\hspace{1em} \theta_{13} = \SI{8.57}{\degree},\hspace{1em} \theta_{23} = \SI{49.2}{\degree}, \hspace{1em} \delta_\text{CP} = 0\,.
\end{align}
with the exception of the CP-violating phase $\delta_\text{CP}$ which we always set to zero for simplicity. The PMNS matrix then has the numerical values 
\begin{align}\label{eq:Uvalues}
    U = \begin{pmatrix}
        U_{e e} & U_{e\mu} & U_{e\tau} \\
        U_{\mu e} & U_{\mu \mu} & U_{\mu \tau} \\
        U_{\tau e} & U_{\tau \mu} & U_{\tau \tau}
    \end{pmatrix} 
    = \begin{pmatrix}
        0.825 & 0.545 & 0.149 \\
        -0.455 & 0.485 & 0.746 \\
        0.334 & -0.684 & 0.649
    \end{pmatrix} \,.
\end{align}
In our study, we will only use atmospheric neutrinos, of which $\nm$ are the most abundant. We see that $U_{\mu\tau}$ is the largest $U_{\mu\beta}$ term,
suggesting that $\nm$ primarily oscillates into $\nt$, at least in vacuum. We will see that matter effects indeed preserves this ordering, making the $\nm \to \nt$ transition
the most abundant. This means we will be able to constrain any parameters relating to $\nm \to \nt$ oscillations stringently.

>>>>

\documentclass[draft=True]{thesis}
\usepackage[margin=0.5in]{geometry}
\usepackage{graphicx, slashed}
\usepackage[utf8]{inputenc}
%\usepackage{hyperref}
\usepackage{xr-hyper}
\externaldocument{SM}
\input{commands}
\begin{document}

@@

In this work, we will be using the best-fit values from~\cite{nufit},
\begin{align}\label{eq:nufitparams}
    &\Delta m^2_{21} =  \SI{7.42e-5}{\electronvolt^2},\hspace{0.5em} \Delta m^2_{31} =  \SI{2.517e-3}{\electronvolt^2}, \nonumber \\
    &\theta_{12} = \SI{33.44}{\degree},\hspace{1em} \theta_{13} = \SI{8.57}{\degree},\hspace{1em} \theta_{23} = \SI{49.2}{\degree}, \hspace{1em} \delta_\text{CP} = 0\,.
\end{align}
with the exception of the CP-violating phase $\delta_\text{CP}$ which we always set to zero for simplicity. The PMNS matrix then has the numerical values 
\begin{align}\label{eq:Uvalues}
    U = \begin{pmatrix}
        U_{e e} & U_{e\mu} & U_{e\tau} \\
        U_{\mu e} & U_{\mu \mu} & U_{\mu \tau} \\
        U_{\tau e} & U_{\tau \mu} & U_{\tau \tau}
    \end{pmatrix} 
    = \begin{pmatrix}
        0.825 & 0.545 & 0.149 \\
        -0.455 & 0.485 & 0.746 \\
        0.334 & -0.684 & 0.649
    \end{pmatrix} \,.
\end{align}
In our study, we will only use atmospheric neutrinos, of which $\nm$ are the most abundant. We see that $U_{\mu\tau}$ is the largest $U_{\mu\beta}$ term,
suggesting that $\nm$ primarily oscillates into $\nt$, at least in vacuum. It turns out that matter effects indeed preserves this ordering, making the $\nm \to \nt$ transition
the most abundant. This means we will be able to stringently constrain parameters relating to $\nm \to \nt$ oscillations.
